---
title: "DS202 HW9"
author: "Craig Orman"
date: "4/7/2022"
output: html_document
---


Link to the [Github Project](https://github.com/ArgentCode/DS202-HW9 "Github Project")
Homework is detailed in [Slides 7-9](https://yumouqiu.github.io/DS202-Spring2022/Practice/practice04.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lubridate)
library(tidyverse)
av = read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)

```

### Question 1 
The avenger data consists of ten columns for each avenger called Death[1-5] to Return[1-5]

Get the data into a format where the five columns for Death[1-5] are replaced by two columnes: Time, and Death. Time should be a number between 1 and 5 (look into the function parse_number); Death is a categorical variables with values “yes”, “no” and "". Call the result deaths.

Similarly, deal with the returns of characters.

```{r}
av0 = av %>% filter(Name.Alias != "")
av1 = av0 %>% gather(key = time, value = death, c(11, 13, 15, 17, 19)) %>% 
  select(Name.Alias, time, death) %>%
  mutate(time = parse_number(time))
av2 = av0 %>% gather(key = time, value = return, c(12, 14, 16, 18, 20)) %>% 
  select(Name.Alias, time, return) %>%
  mutate(time = parse_number(time))
av.neat = left_join(av1, av2, by = c("Name.Alias", "time"))
av0 = av0 %>% filter(Name.Alias != "Vance Astrovik")
av1 = av0 %>% gather(key = time, value = death, c(11, 13, 15, 17, 19)) %>% 
  select(Name.Alias, time, death) %>%
  mutate(time = parse_number(time))
av2 = av0 %>% gather(key = time, value = return, c(12, 14, 16, 18, 20)) %>% 
  select(Name.Alias, time, return) %>%
  mutate(time = parse_number(time))
av.neat = left_join(av1, av2, by = c("Name.Alias", "time"))
```

#### 1 answer

We completed this question as an inclass lab.

### Question 2

Each team member picks one of the statements in the FiveThirtyEight [analysis](https://fivethirtyeight.com/features/avengers-death-comics-age-of-ultron/) and fact checks it based on the data. Use dplyr functionality whenever possible.

Upload your answers and the code to the repository. Discuss and refine answers as a team.

#### Craig's Question:

"But you can only tempt death so many times. There’s a 2-in-3 chance that a member of the Avengers returned from their first stint in the afterlife, but only a 50 percent chance they recovered from a second or third death." This is a claim made from the writer of the article. Seems like it will involve a variety of tasks to find the answer to. 

Question: What is the chance an Avenger will return after they die the first, second, and third time they die. That's a weird research question but okay.

```{r}
av.neat3 = av.neat %>% mutate(
  death = as.factor(death),
  return = as.factor(return)
)
av.neat3 = av.neat3 %>% filter(death == "YES")
first.death.rate = av.neat3 %>% filter(time == 1) %>% filter(return == "YES") %>% count() / av.neat3 %>% filter(time == 1)%>% count() 
first.death.rate$deaths = av.neat3 %>% filter(time == 1)%>% count()
first.death.rate$returns = av.neat3 %>% filter(time == 1) %>% filter(return == "YES") %>% count()
first.death.rate$time = 1

first.death.rate2 = av.neat3 %>% filter(time == 2) %>% filter(return == "YES") %>% count() / av.neat3 %>% filter(time == 2)%>% count() 
first.death.rate2$deaths = av.neat3 %>% filter(time == 2)%>% count()
first.death.rate2$returns = av.neat3 %>% filter(time == 2) %>% filter(return == "YES") %>% count()
first.death.rate2$time = 2

first.death.rate3 = av.neat3 %>% filter(time == 3) %>% filter(return == "YES") %>% count() / av.neat3 %>% filter(time == 3)%>% count()
first.death.rate3$deaths = av.neat3 %>% filter(time == 3)%>% count()
first.death.rate3$returns = av.neat3 %>% filter(time == 3) %>% filter(return == "YES") %>% count() 
first.death.rate3$time = 3

first.death.rate4 = av.neat3 %>% filter(time == 4) %>% filter(return == "YES") %>% count() / av.neat3 %>% filter(time == 4)%>% count() 
first.death.rate4$deaths = av.neat3 %>% filter(time == 4)%>% count()
first.death.rate4$returns = av.neat3 %>% filter(time == 4) %>% filter(return == "YES") %>% count()
first.death.rate4$time = 4

first.death.rate5 = av.neat3 %>% filter(time == 5) %>% filter(return == "YES") %>% count() / av.neat3 %>% filter(time == 5)%>% count() 
first.death.rate5$deaths = av.neat3 %>% filter(time == 5)%>% count()
first.death.rate5$returns = av.neat3 %>% filter(time == 5) %>% filter(return == "YES") %>% count()
first.death.rate5$time = 5

results = first.death.rate
results = rbind(results, first.death.rate2)
results = rbind(results, first.death.rate3)
results = rbind(results, first.death.rate4)
results = rbind(results, first.death.rate5)

```



```{r}
results = av.neat %>%
  group_by(time) %>%
  summarise( total.num = n(),
             real.death = sum(death == "YES"),
             fake.death = sum(death == "NO"),
             missing = sum(death == ""),
             real.return = sum(return == "YES"),
             no.return = sum(return == "NO"),
             return.rate = real.return/real.death
             )

```




